\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-05-26 manuscript.tex

\textbf{Evidence of introgression---}The highest frequency of the \emph{Hopscotch} insertion in teosinte was found in \emph{parviglumis} sympatric with cultivated maize. Our initial hypothesis was that the high frequency of the \emph{Hopscotch} element in these populations could be attributed to introgression from maize into teosinte. To investigate this possibility we examined overall patterns of linkage disequilibrium across chromosome one and specifically in the \emph{tb1} region. If the \emph{Hopscotch} is found in these populations due to recent introgression we would expect to find large blocks of linked markers near this element. We find no evidence of elevated linkage disequilibrium between the \emph{Hopscotch} and SNPs surrounding the \emph{tb1} region in our resequenced populations (Fig. \ref{Fig2LD}), and $r^{2}$ in the \emph{tb1} region  does not differ significantly between populations with (average $r^{2}$ of 0.085) and without (average $r^{2}=0.082$) the \emph{Hopscotch} insertion. In fact, average $r^{2}$ is lower in the \emph{tb1} region ($r^{2}=0.056$) than across the rest of chromosome 1 ($r^{2}=0.083$) (\ref{Table3R2}). \mbh{LV, please go through and make sure the data entered into all the tables is correct.  In Table3, both sequenced regions were labeled as "Region 1".  I changed the second to Region 2 but don't know if the data in this column are really from Region 2}

@@

% Figure 2. LD plots
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=140mm]{Fig2LDPlots.pdf}
    \caption{Linkage disequilibrium for SNPs in Mb 261-268 on chromosome 1. The yellow rectangle indicates the location of the \emph{Hopscotch} insertion and the green represents the \emph{tb1} ORF. A) Ejutla A; B) Ejutla B; C) La Mesa; D). San Lorenzo}  \jri{this needs description of what upper and lower triangle are}
\label{Fig2LD}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

@@

% Figure 4 Phenotyping BoxPlots
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=95mm]{Fig4Boxplots.pdf}
    \caption{Box-plots showing tillering index in greenhouse grow-outs for Phenotyping 1 (A) and Phenotyping 2 (B). White indicates individuals homozygous for the \emph{Hopscotch}, light grey represents heterozygotes, and dark grey represents homozygotes for the teosinte (No \emph{Hopscotch}) allele. Within boxes, dark black lines represent the median, and the edges of the boxes are the first and third quartiles. \jri{please explain whiskers and dots on figure too.}} 
\label{Fig4Boxplots}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

@@

\jri{please check format of supp figs and tables; some are running off the page.  you can use "longtable" to fix that (ask Paul for example). check fig/table references, bibliography, etc. what does "rotation" mean in supp. table 3? it isn't mentioned in methods. please check that all the tables and figs (including supplement) are referenced in the text.}

@@

%-------------------------------------------------
Supplementary Materials
%-------------------------------------------------
\clearpage
\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand{\figurename}{Sup.\Fig.}
\renewcommand{\tablename}{Sup.\Table}

% Figure S1. Cartoon representation of tb1 locus
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=140mm]{FigS1LocusCartoon.pdf}
  %\caption{Representation of the upstream regulatory region of \emph{tb1}, showing the \emph{tb1} coding region (green) and the \emph{Hopscotch} insertion (red). Arrows show the location of primer sets; in black, primers used for amplification and sequencing (Sequenced region 1; within the 5' UTR, and sequenced region 2; 66,169 bp upstream from the tb1 ORF); in blue, primers used to genotype the \emph{Hopscotch} insertion.}
\label{FigS1Locus}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

% Figure S2. Gel image
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=150mm]{FigS2Gel.png}
   % \caption{Agarose gel image of amplification products using our primer sets. Genotypes are indicated at the top of the gel.} 
\label{FigS2Gel}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

% Figure S3. NJ Trees
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=150mm]{FigS3NJtrees.pdf}
    %\caption{Neighbor-Joining tree of the sequenced region in the 5? UTR (right; sequenced region 1) and the 66,169 bp upstream region (left; sequenced region 2) of \emph{tb1}. Individuals with genotype data are colored: Homozygous for the teosinte (no \emph{Hopscotch}) allele (red), homozygous for the maize (\emph{Hopscotch}) allele (blue), heterozygotes (purple). TILs (teosinte inbred lines) are colored in green, with stars indicating the 3 TILs known to have the \emph{Hopscotch} insertion. Black indicates individuals not genotyped for the \emph{Hopscotch} insertion.} 
\label{FigS3NJ}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

% Table S1. Parv and mex samples
\begin{table}[htbp]
  \centering
  %\caption{Accessions of \emph{Zea mays} ssp. \emph{mexicana} (RIMME) and \emph{Zea mays} ssp. \emph{parviglumis} (RIMPA) sampled. RIHY is a \emph{Z. mays} ssp. \emph{parviglumis} and \emph{Zea mays} ssp. \emph{mays} hybrid. }
    \begin{tabular}{rrrrrr}
%    \toprule
    Accession & USDA Accession ID & Locality & Number alleles sampled & \emph{Hopscotch} Frequency & No \emph{Hopscotch} Frequency \\
 %   \midrule
    RIHY0009 & N/A   & N/A   & 2     & 0.5   & 0.5 \\
    RIMME0006 & 566673 & Durango, Mexico & 2     & 0     & 1 \\
    RIMME0007 & 566680 & Guanajuato, Mexico & 2     & 0     & 1 \\
    RIMME0008 & 566681 & Michoacan, Mexico & 2     & 0     & 1 \\
    RIMME0009 & 566682 & Distrito Federal, Mexico & 2     & 0     & 1 \\
    RIMME0011 & 566685 & Mexico, Mexico & 2     & 0     & 1 \\
    RIMME0014 & 714151 & Breeders line; Puga: 11066 & 6     & 0     & 1 \\
    RIMME0017 & 699874 & Ayotlan, Mexico & 8     & 0     & 1 \\
    RIMME0021 & N/A   & El Porvenir, Mexico & 69    & 0.173913043 & 0.826086957 \\
    RIMME0026 & N/A   & Opopeo, Mexico & 42    & 0.071428571 & 0.928571429 \\
    RIMME0028 & N/A   & Puruandiro, Mexico & 28    & 0.035714286 & 0.964285714 \\
    RIMME0029 & N/A   & Ixtlan, Mexico & 35    & 0     & 1 \\
    RIMME0030 & N/A   & San Pedro, Mexico & 27    & 0     & 1 \\
    RIMME0031 & N/A   & Tenango del Aire, Mexico & 25    & 0.08  & 0.92 \\
    RIMME0032 & N/A   & Nabogame, Mexico & 24    & 0     & 1 \\
    RIMME0033 & N/A   & Puerta Encantada, Mexico & 25    & 0     & 1 \\
    RIMME0034 & N/A   & Santa Clara, Mexico & 23    & 0     & 1 \\
    RIMME0035 & N/A   & Xochimilco, Mexico & 25    & 0     & 1 \\
    RIMPA0001 & 87168 & El Salado, Mexico & 4     & 0     & 1 \\
    RIMPA0003 & 87171 & Mazatlan, Mexico & 8     & 0.125 & 0.875 \\
    RIMPA0017 & 87200 & N/A   & 4     & 0     & 1 \\
    RIMPA0019 & 87213 & El Salado, Mexico & 2     & 0.5   & 0.5 \\
    RIMPA0029 & 87244 & N/A   & 2     & 0.5   & 0.5 \\
    RIMPA0031 & 87249 & N/A   & 2     & 0.5   & 0.5 \\
    RIMPA0035 & 87288 & Jalisco, Mexico & 4     & 0     & 1 \\
    RIMPA0040 & 288185 & Mexico, Mexico & 4     & 0     & 1 \\
    RIMPA0042 & 288187 & Guerrero, Mexico & 4     & 0.25  & 0.75 \\
    RIMPA0043 & 288188 & Guerrero, Mexico & 4     & 0     & 1 \\
    RIMPA0045 & 288193 & Guerrero, Mexico & 4     & 0     & 1 \\
    RIMPA0055 & 714152 & Breeders line & 2     & 0     & 1 \\
    RIMPA0056 & 714153 & Breeders line & 2     & 0.5   & 0.5 \\
    RIMPA0057 & 714154 & Breeders line & 2     & 0.5   & 0.5 \\
    RIMPA0058 & N/A   & N/A   & 4     & 0.5   & 0.5 \\
    RIMPA0059 & N/A   & N/A   & 4     & 1     & 0 \\
    RIMPA0060 & 714157 & Breeders line: CIMMYT 11355 & 2     & 0     & 1 \\
    RIMPA0061 & 714158 & Breeders line: USDA PI566686 & 4     & 0.5   & 0.5 \\
    RIMPA0062 & 714159 & Breeders line & 4     & 0.5   & 0.5 \\
    RIMPA0063 & 714160 & Breeders line & 4     & 0     & 1 \\
    RIMPA0064 & 714161 & Breeders line & 3     & 0     & 1 \\
    RIMPA0065 & 714162 & Breeders line & 4     & 0.25  & 0.75 \\
    RIMPA0068 & 699861 & Jalisco, Mexico & 16    & 0     & 1 \\
    RIMPA0069 & 699862 & Ixtlan, Mexico & 14    & 0.142857143 & 0.857142857 \\
    RIMPA0070 & 699863 & Benito Jaurez, Mexico & 16    & 0     & 1 \\
    RIMPA0071 & 699864 & Tuzantla, Mexico & 28    & 0     & 1 \\
    RIMPA0072 & 699865 & Tiquicheo, Mexico & 16    & 0     & 1 \\
    RIMPA0073 & 699866 & Tiquicheo, Mexico & 16    & 0.125 & 0.875 \\
    RIMPA0074 & 699867 & Huetamo, Mexico & 12    & 0     & 1 \\
    RIMPA0075 & 699868 & Huetamo, Mexico & 2     & 0     & 1 \\
    RIMPA0076 & 699869 & Huetamo, Mexico & 4     & 0     & 1 \\
    RIMPA0077 & 699870 & Caracuaro, Mexico & 2     & 0     & 1 \\
    RIMPA0078 & 699871 & Caracuaro, Mexico & 2     & 0.5   & 0.5 \\
    RIMPA0079 & 699872 & Villa Madero, Mexico & 14    & 0     & 1 \\
    RIMPA0080 & 699873 & Guachinango, Mexico & 12    & 0     & 1 \\
    RIMPA0081 & 699875 & Ameca, Mexico & 16    & 0     & 1 \\
    RIMPA0083 & 699877 & Tepoztlan, Mexico & 14    & 0     & 1 \\
    RIMPA0084 & 699878 & Tepoztlan, Mexico & 16    & 0     & 1 \\
    RIMPA0085 & 699879 & Miahuatlan, Mexico & 16    & 0     & 1 \\
    RIMPA0086 & 699880 & Miahuatlan, Mexico & 16    & 0.0625 & 0.9375 \\
    RIMPA0087 & 699881 & Tecoanapa, Mexico & 24    & 0     & 1 \\
    RIMPA0089 & 699883 & Guerrero, Mexico & 12    & 0     & 1 \\
    RIMPA0090 & 699884 & Guerrero, Mexico & 10    & 0     & 1 \\
    RIMPA0091 & 699885 & Guerrero, Mexico & 16    & 0     & 1 \\
    RIMPA0092 & 699886 & Guerrero, Mexico & 10    & 0     & 1 \\
    RIMPA0093 & 699887 & Guerrero, Mexico & 26    & 0.076923077 & 0.923076923 \\
    RIMPA0094 & 699888 & Guerrero, Mexico & 2     & 0     & 1 \\
    RIMPA0095 & 699889 & Guerrero, Mexico & 4     & 0     & 1 \\
    RIMPA0096 & 699890 & Guerrero, Mexico & 26    & 0.038461538 & 0.961538462 \\
    RIMPA0097 & 699891 & Guerrero, Mexico & 6     & 0     & 1 \\
    RIMPA0098 & 699892 & Guerrero, Mexico & 4     & 0     & 1 \\
    RIMPA0099 & 699893 & Guerrero, Mexico & 4     & 0     & 1 \\
    RIMPA0100 & 699894 & Guerrero, Mexico & 6     & 0     & 1 \\
    RIMPA0101 & 699895 & Guerrero, Mexico & 2     & 0     & 1 \\
    RIMPA0103 & 699897 & Guerrero, Mexico & 2     & 0     & 1 \\
    RIMPA0104 & 699898 & Guerrero, Mexico & 22    & 0.090909091 & 0.909090909 \\
    RIMPA0105 & 699899 & Guerrero, Mexico & 6     & 0     & 1 \\
    RIMPA0106 & 699900 & Guerrero, Mexico & 6     & 0.333333333 & 0.666666667 \\
    RIMPA0107 & 699901 & Guerrero, Mexico & 4     & 0     & 1 \\
    RIMPA0108 & 699902 & Guerrero, Mexico & 6     & 0     & 1 \\
    RIMPA0109 & 699903 & Michoacan, Mexico & 4     & 0.25  & 0.75 \\
    RIMPA0110 & 699904 & Michoacan, Mexico & 2     & 0     & 1 \\
    RIMPA0111 & 699905 & Michoacan, Mexico & 4     & 0     & 1 \\
    RIMPA0112 & 699906 & Michoacan, Mexico & 4     & 0.25  & 0.75 \\
    RIMPA0114 & 699908 & Michoacan, Mexico & 6     & 0.166666667 & 0.833333333 \\
    RIMPA0116 & 699910 & Mexico, Mexico & 2     & 0     & 1 \\
    RIMPA0117 & 699911 & Mexico, Mexico & 4     & 0     & 1 \\
    RIMPA0118 & 699912 & Mexico, Mexico & 6     & 0.166666667 & 0.833333333 \\
    RIMPA0119 & 699913 & Mexico, Mexico & 2     & 0     & 1 \\
    RIMPA0120 & 699914 & Mexico, Mexico & 1     & 1     & 0 \\
    RIMPA0121 & 699915 & Mexico, Mexico & 2     & 0     & 1 \\
    RIMPA0128 & 699922 & Mexico, Mexico & 2     & 0.5   & 0.5 \\
    RIMPA0129 & 699923 & Michoacan, Mexico & 2     & 0.5   & 0.5 \\
    RIMPA0135 & 699929 & Nayarit, Mexico & 24    & 0     & 1 \\
    RIMPA0138 & 699932 & Jalisco, Mexico & 2     & 0.5   & 0.5 \\
    RIMPA0139 & 699933 & Jalisco, Mexico & 1     & 1     & 0 \\
    RIMPA0142 & 699936 & Colima, Mexico & 18    & 0.444444444 & 0.555555556 \\
    RIMPA0144 & 699938 & Jalisco, Mexico & 2     & 1     & 0 \\
    RIMPA0145 & 699939 & Michoacan, Mexico & 1     & 1     & 0 \\
    RIMPA0147 & 699941 & Jalisco, Mexico & 1     & 1     & 0 \\
    RIMPA0155 & N/A   & Jalisco, Mexico & 73    & 0.01369863 & 0.98630137 \\
    RIMPA0156 & N/A   & Jalisco, Mexico & 20    & 0     & 1 \\
    RIMPA0157 & N/A   & Jalisco, Mexico & 58    & 0.344827586 & 0.655172414 \\
    RIMPA0158 & N/A   & Jalisco, Mexico & 64    & 0.53125 & 0.46875 \\
    RIMPA0159 & N/A   & Jalisco, Mexico & 26    & 0     & 1 \\
    RIMPA0162 & 21785 & N/A   & 4     & 0     & 1 \\
 %   \bottomrule
    \end{tabular}
  \label{TableS1}
\end{table}

% Table S2. Mays sampling
\begin{table}[htbp]
  \centering
 % \caption{\emph{Zea mays} ssp. \emph{mays} (RIMMA) sampled for genotyping}
    \begin{tabular}{ccc}
 %   \toprule
    Accession & Number of alleles sampled & \emph{Hopscotch} Frequency \\
 %   \midrule
    RIMMA0066 & 2     & 1 \\
    RIMMA0075 & 2     & 1 \\
    RIMMA0077 & 2     & 1 \\
    RIMMA0079 & 2     & 1 \\
    RIMMA0081 & 2     & 1 \\
    RIMMA0084 & 2     & 1 \\
    RIMMA0086 & 2     & 1 \\
    RIMMA0088 & 2     & 1 \\
    RIMMA0089 & 2     & 1 \\
    RIMMA0090 & 2     & 1 \\
    RIMMA0092 & 4     & 1 \\
    RIMMA0094 & 4     & 1 \\
    RIMMA0097 & 2     & 1 \\
    RIMMA0099 & 2     & 1 \\
    RIMMA0100 & 2     & 1 \\
    RIMMA0101 & 2     & 1 \\
    RIMMA0104 & 2     & 1 \\
    RIMMA0108 & 2     & 1 \\
    RIMMA0111 & 6     & 1 \\
    RIMMA0115 & 2     & 1 \\
    RIMMA0117 & 2     & 1 \\
    RIMMA0130 & 2     & 1 \\
    RIMMA0133 & 2     & 1 \\
    RIMMA0134 & 2     & 1 \\
    RIMMA0135 & 2     & 1 \\
    RIMMA0142 & 2     & 0.5 \\
    RIMMA0143 & 4     & 1 \\
    RIMMA0146 & 4     & 1 \\
    RIMMA0149 & 2     & 1 \\
    RIMMA0152 & 2     & 1 \\
    RIMMA0153 & 2     & 1 \\
    RIMMA0154 & 2     & 1 \\
    RIMMA0155 & 2     & 1 \\
    RIMMA0156 & 2     & 1 \\
    RIMMA0157 & 2     & 1 \\
    RIMMA0158 & 2     & 1 \\
    RIMMA0159 & 2     & 1 \\
    RIMMA0160 & 2     & 1 \\
    RIMMA0162 & 2     & 1 \\
    RIMMA0166 & 2     & 1 \\
    RIMMA0167 & 2     & 1 \\
    RIMMA0168 & 2     & 1 \\
    RIMMA0169 & 2     & 1 \\
    RIMMA0172 & 2     & 1 \\
    RIMMA0174 & 4     & 1 \\
    RIMMA0177 & 2     & 1 \\
    RIMMA0178 & 2     & 1 \\
    RIMMA0179 & 2     & 1 \\
    RIMMA0181 & 2     & 1 \\
    RIMMA0183 & 2     & 1 \\
    RIMMA0184 & 2     & 1 \\
    RIMMA0186 & 2     & 1 \\
    RIMMA0187 & 1     & 1 \\
    RIMMA0188 & 2     & 1 \\
    RIMMA0195 & 2     & 1 \\
    RIMMA0196 & 2     & 1 \\
    RIMMA0197 & 2     & 1 \\
    RIMMA0198 & 2     & 1 \\
    RIMMA0199 & 2     & 1 \\
    RIMMA0200 & 2     & 1 \\
    RIMMA0202 & 2     & 1 \\
    RIMMA0203 & 2     & 1 \\
    RIMMA0206 & 2     & 1 \\
    RIMMA0208 & 2     & 1 \\
    RIMMA0209 & 2     & 1 \\
    RIMMA0210 & 2     & 1 \\
    RIMMA0212 & 2     & 1 \\
    RIMMA0213 & 2     & 1 \\
    RIMMA0214 & 2     & 1 \\
    RIMMA0217 & 2     & 1 \\
    RIMMA0218 & 2     & 1 \\
    RIMMA0220 & 2     & 1 \\
    RIMMA0221 & 2     & 1 \\
    RIMMA0222 & 2     & 1 \\
    RIMMA0223 & 2     & 1 \\
    RIMMA0226 & 2     & 1 \\
    RIMMA0227 & 2     & 1 \\
    RIMMA0228 & 2     & 1 \\
    RIMMA0229 & 2     & 1 \\
    RIMMA0230 & 2     & 1 \\
    RIMMA0232 & 2     & 1 \\
    RIMMA0233 & 2     & 1 \\
    RIMMA0235 & 2     & 0.5 \\
    RIMMA0242 & 2     & 1 \\
    RIMMA0243 & 2     & 1 \\
    RIMMA0247 & 4     & 1 \\
    RIMMA0248 & 2     & 1 \\
    RIMMA0249 & 2     & 1 \\
    RIMMA0252 & 2     & 1 \\
    RIMMA0253 & 2     & 1 \\
    RIMMA0254 & 2     & 1 \\
    RIMMA0256 & 2     & 1 \\
    RIMMA0257 & 2     & 1 \\
    RIMMA0258 & 2     & 1 \\
    RIMMA0259 & 2     & 1 \\
    RIMMA0260 & 2     & 1 \\
    RIMMA0262 & 2     & 1 \\
    RIMMA0263 & 2     & 1 \\
    RIMMA0264 & 2     & 1 \\
    RIMMA0265 & 2     & 1 \\
    RIMMA0268 & 2     & 1 \\
    RIMMA0269 & 2     & 1 \\
    RIMMA0270 & 2     & 1 \\
    RIMMA0272 & 2     & 1 \\
    RIMMA0275 & 2     & 1 \\
    RIMMA0276 & 2     & 1 \\
    RIMMA0277 & 2     & 1 \\
    RIMMA0279 & 2     & 1 \\
    RIMMA0280 & 2     & 1 \\
    RIMMA0283 & 2     & 1 \\
    RIMMA0285 & 2     & 1 \\
    RIMMA0288 & 2     & 1 \\
    RIMMA0290 & 2     & 1 \\
    RIMMA0291 & 2     & 1 \\
    RIMMA0292 & 2     & 1 \\
    RIMMA0293 & 2     & 1 \\
    RIMMA0298 & 2     & 1 \\
    RIMMA0302 & 2     & 1 \\
    RIMMA0305 & 2     & 1 \\
    RIMMA0310 & 2     & 1 \\
    RIMMA0312 & 2     & 1 \\
    RIMMA0320 & 2     & 1 \\
    RIMMA0322 & 2     & 1 \\
    RIMMA0324 & 2     & 1 \\
    RIMMA0334 & 2     & 1 \\
    RIMMA0336 & 2     & 1 \\
    RIMMA0337 & 2     & 1 \\
    RIMMA0338 & 2     & 1 \\
    RIMMA0339 & 2     & 1 \\
    RIMMA0340 & 2     & 1 \\
    RIMMA0341 & 2     & 1 \\
    RIMMA0342 & 2     & 1 \\
    RIMMA0344 & 2     & 1 \\
    RIMMA0346 & 2     & 1 \\
    RIMMA0347 & 2     & 1 \\
    RIMMA0350 & 2     & 1 \\
    RIMMA0351 & 2     & 1 \\
    RIMMA0352 & 2     & 1 \\
    RIMMA0357 & 2     & 1 \\
    RIMMA0360 & 18    & 1 \\
    RIMMA0362 & 8     & 1 \\
    RIMMA0363 & 16    & 1 \\
    RIMMA0370 & 17    & 1 \\
    RIMMA0372 & 24    & 1 \\
    RIMMA0373 & 22    & 1 \\
    RIMMA0408 & 2     & 1 \\
    RIMMA0411 & 1     & 1 \\
    RIMMA0413 & 1     & 1 \\
    RIMMA0414 & 1     & 1 \\
    RIMMA0424 & 8     & 0.9 \\
    RIMMA0432 & 1     & 1 \\
    RIMMA0434 & 2     & 0.5 \\
    RIMMA0435 & 1     & 1 \\
    RIMMA0442 & 2     & 1 \\
    RIMMA0443 & 2     & 1 \\
    RIMMA0444 & 2     & 1 \\
    RIMMA0445 & 2     & 1 \\
    RIMMA0446 & 2     & 1 \\
    RIMMA0447 & 2     & 1 \\
    RIMMA0448 & 2     & 1 \\
    RIMMA0449 & 2     & 1 \\
    RIMMA0450 & 2     & 1 \\
    RIMMA0451 & 2     & 1 \\
    RIMMA0452 & 2     & 1 \\
    RIMMA0453 & 2     & 1 \\
    RIMMA0454 & 2     & 1 \\
    RIMMA0455 & 2     & 1 \\
    RIMMA0456 & 2     & 1 \\
    RIMMA0457 & 2     & 1 \\
    RIMMA0458 & 2     & 1 \\
    RIMMA0459 & 2     & 1 \\
    RIMMA0483 & 2     & 1 \\
    RIMMA0490 & 2     & 1 \\
    RIMMA0515 & 2     & 1 \\
    RIMMA0537 & 2     & 1 \\
    RIMMA0550 & 2     & 1 \\
    RIMMA0553 & 2     & 1 \\
    RIMMA0559 & 2     & 1 \\
    RIMMA0561 & 2     & 1 \\
    RIMMA0562 & 2     & 1 \\
    RIMMA0571 & 2     & 1 \\
    RIMMA0572 & 2     & 1 \\
    RIMMA0577 & 2     & 1 \\
    RIMMA0579 & 2     & 1 \\
    RIMMA0590 & 2     & 1 \\
    RIMMA0591 & 2     & 1 \\
    RIMMA0592 & 2     & 1 \\
    RIMMA0593 & 2     & 1 \\
    RIMMA0594 & 2     & 1 \\
    RIMMA0595 & 2     & 1 \\
    RIMMA0596 & 2     & 1 \\
    RIMMA0597 & 2     & 1 \\
    RIMMA0598 & 2     & 1 \\
    RIMMA0599 & 2     & 1 \\
    RIMMA0600 & 2     & 1 \\
    RIMMA0601 & 2     & 1 \\
    RIMMA0602 & 2     & 1 \\
    RIMMA0603 & 2     & 1 \\
    RIMMA0604 & 2     & 1 \\
    RIMMA0605 & 2     & 1 \\
    RIMMA0606 & 2     & 1 \\
    RIMMA0607 & 2     & 1 \\
    RIMMA0608 & 2     & 1 \\
    RIMMA0609 & 2     & 1 \\
    RIMMA0610 & 2     & 1 \\
    RIMMA0611 & 2     & 1 \\
    RIMMA0612 & 2     & 1 \\
    RIMMA0613 & 2     & 1 \\
    RIMMA0622 & 2     & 0.5 \\
    RIMMA0624 & 1     & 1 \\
    RIMMA0629 & 2     & 0.5 \\
    RIMMA0631 & 2     & 0.5 \\
    RIMMA0659 & 2     & 1 \\
    RIMMA0660 & 2     & 1 \\
    RIMMA0678 & 1     & 1 \\
    RIMMA0681 & 2     & 1 \\
    RIMMA0683 & 2     & 1 \\
    RIMMA0684 & 2     & 1 \\
    RIMMA0685 & 4     & 1 \\
    RIMMA0693 & 2     & 1 \\
    RIMMA0694 & 2     & 1 \\
    RIMMA0695 & 1     & 1 \\
    RIMMA0699 & 2     & 1 \\
    RIMMA0704 & 2     & 1 \\
    RIMMA0706 & 2     & 1 \\
    RIMMA0711 & 1     & 1 \\
    RIMMA0713 & 2     & 1 \\
    RIMMA0715 & 2     & 1 \\
    RIMMA0717 & 2     & 1 \\
    RIMMA0718 & 2     & 1 \\
    RIMMA0723 & 2     & 1 \\
    RIMMA0724 & 2     & 1 \\
    RIMMA0725 & 1     & 1 \\
    RIMMA0728 & 1     & 1 \\
    RIMMA0732 & 2     & 1 \\
    RIMMA0734 & 2     & 1 \\
    RIMMA0738 & 2     & 1 \\
    RIMMA0739 & 2     & 1 \\
    RIMMA0744 & 2     & 1 \\
    RIMMA0747 & 1     & 1 \\
    RIMMA0748 & 2     & 1 \\
    RIMMA0749 & 2     & 1 \\
    RIMMA0750 & 2     & 0.5 \\
    RIMMA0751 & 1     & 1 \\
    RIMMA0752 & 1     & 1 \\
    RIMMA0753 & 2     & 1 \\
    RIMMA0755 & 2     & 1 \\
    \bottomrule
    \end{tabular}
  \label{TableS2Mays}
\end{table}

% Table S3. PCs for BayEnv
\begin{table}[htbp]
  \centering
  %\caption{Variables and rotations used for the 6 principal components used for BayEnv calculations and their corresponding Bayes Factors. Modified from \citet{Pyhajarvi2013}.}
    \begin{tabular}{rrrrrrrrrrrr}
    \toprule
    \textbf{PC1} & \textbf{} & \textbf{PC2} & \textbf{} & \textbf{PC3} & \textbf{} & \textbf{PC4} & \textbf{} & \textbf{PC5} & \textbf{} & \textbf{PC6} & \textbf{} \\
    \midrule
    \textbf{Var} & \textbf{Rot} & \textbf{Var} & \textbf{Rot} & \textbf{Var} & \textbf{Rot} & \textbf{Var} & \textbf{Rot} & \textbf{Var} & \textbf{Rot} & \textbf{Var} & \textbf{Rot} \\
    bio1  & 0.146 & bio4  & 0.244 & prec7 & 0.287 & ts\_clay & 0.41  & bio2  & 0.38  & bio2  & 0.412 \\
    tmean11 & 0.146 & bio3  & 0.241 & prec8 & 0.276 & v\_mod & 0.359 & sq4   & 0.328 & x\_mod & 0.365 \\
    tmean12 & 0.145 & bio7  & 0.241 & prec11 & 0.262 & ts\_sand & 0.329 & ts\_loam & 0.289 & sq7   & 0.332 \\
    bio11 & 0.145 & prec6 & 0.237 & bio13 & 0.247 & bio15 & 0.272 & ts\_sand & 0.266 & bio7  & 0.312 \\
    tmax12 & 0.145 & sq7   & 0.218 & prec1 & 0.246 & prec4 & 0.259 & sq7   & 0.231 & v\_mod & 0.307 \\
    tmin5 & 0.145 & prec9 & 0.217 & bio16 & 0.242 & x\_mod & 0.244 & bio18 & 0.213 & prec11 & 0.23 \\
    tmean1 & 0.145 & sq3   & 0.207 & prec12 & 0.24  & prec3 & 0.226 & bio13 & 0.207 & bio18 & 0.22 \\
    tmean2 & 0.145 & prec12 & 0.207 & bio19 & 0.238 & sq3   & 0.21  & prec11 & 0.183 & sq3   & 0.176 \\
    tmin4 & 0.145 & bio12 & 0.204 & bio12 & 0.231 & prec5 & 0.21  & bio7  & 0.17  & sq4   & 0.153 \\
    tmax1 & 0.145 & bio19 & 0.196 & prec2 & 0.222 & prec7 & 0.19  & bio16 & 0.163 & ts\_sand & 0.153 \\
    tmean4 & 0.145 & prec2 & 0.188 & bio18 & 0.221 & sq4   & 0.186 & bio4  & 0.157 & bio4  & 0.148 \\
    tmin11 & 0.144 & prec1 & 0.185 & sq4   & 0.2   & bio3  & 0.185 & bio12 & 0.156 & prec7 & 0.139 \\
    tmax11 & 0.144 & prec10 & 0.184 & prec9 & 0.18  & bio18 & 0.178 & bio3  & 0.155 & tmax3 & 0.127 \\
    tmin12 & 0.144 & bio16 & 0.183 & prec10 & 0.171 & sq7   & 0.132 & prec6 & 0.154 & tmax4 & 0.126 \\
    tmin2 & 0.144 & prec8 & 0.17  & prec5 & 0.161 & bio14 & 0.116 & x\_mod & 0.152 & bio5  & 0.118 \\
    tmean5 & 0.144 & prec5 & 0.165 & prec4 & 0.154 & bio13 & 0.099 & prec9 & 0.144 & tmax5 & 0.115 \\
    tmean10 & 0.144 & bio14 & 0.158 & sq3   & 0.147 & bio16 & 0.095 & prec8 & 0.143 & bio3  & 0.107 \\
    bio6  & 0.144 & bio13 & 0.151 & bio2  & 0.143 & prec8 & 0.09  & v\_mod & 0.142 & ts\_loam & 0.095 \\
    tmax2 & 0.144 & bio17 & 0.149 & bio17 & 0.129 & bio7  & 0.077 & bio15 & 0.136 & ts\_clay & 0.078 \\
    tmean3 & 0.144 & prec3 & 0.144 & ts\_loam & 0.127 & bio4  & 0.075 & prec7 & 0.112 & tmin9 & 0.072 \\
    tmin1 & 0.143 & ts\_clay & 0.141 & v\_mod & 0.123 & bio2  & 0.074 & prec4 & 0.108 & tmin8 & 0.071 \\
    tmin10 & 0.143 & bio2  & 0.129 & prec3 & 0.113 & prec2 & 0.074 & bio14 & 0.096 & prec9 & 0.07 \\

>>>>

\textbf{Evidence of introgression---}The highest frequency of the \emph{Hopscotch} insertion in teosinte was found in \emph{parviglumis} sympatric with cultivated maize. Our initial hypothesis was that the high frequency of the \emph{Hopscotch} element in these populations could be attributed to introgression from maize into teosinte. To investigate this possibility we examined overall patterns of linkage disequilibrium across chromosome one and specifically in the \emph{tb1} region. If the \emph{Hopscotch} is found in these populations due to recent introgression we would expect to find large blocks of linked markers near this element. We find no evidence of elevated linkage disequilibrium between the \emph{Hopscotch} and SNPs surrounding the \emph{tb1} region in our resequenced populations (Fig. \ref{Fig2LD}), and $r^{2}$ in the \emph{tb1} region  does not differ significantly between populations with (average $r^{2}$ of 0.085) and without (average $r^{2}=0.082$) the \emph{Hopscotch} insertion. In fact, average $r^{2}$ is lower in the \emph{tb1} region ($r^{2}=0.056$) than across the rest of chromosome 1 ($r^{2}=0.083$) (\ref{Table3R2}).

@@

% Figure 2. LD plots
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=140mm]{Fig2LDPlots.pdf}
    \caption{Linkage disequilibrium for SNPs in Mb 261-268 on chromosome 1. The yellow rectangle indicates the location of the \emph{Hopscotch} insertion and the green represents the \emph{tb1} ORF. A) Ejutla A; B) Ejutla B; C) La Mesa; D). San Lorenzo}. The upper triangle above the black diagonal is colored based on the $r^{2}$ value between SNPs while the bottom triangle is colored based on p-value for the corresponding  $r^{2}$ value.  
\label{Fig2LD}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

@@

% Figure 4 Phenotyping BoxPlots
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=95mm]{Fig4Boxplots.pdf}
    \caption{Box-plots showing tillering index in greenhouse grow-outs for Phenotyping 1 (A) and Phenotyping 2 (B). White indicates individuals homozygous for the \emph{Hopscotch}, light grey represents heterozygotes, and dark grey represents homozygotes for the teosinte (No \emph{Hopscotch}) allele. Within boxes, dark black lines represent the median, and the edges of the boxes are the first and third quartiles. Outliers are displayed as dots, the maximum value exluding outliers is shown with the top whisker, whicle the minimum exlucing outliers is shown with the bottom whisker.
\label{Fig4Boxplots}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

@@

\lev{I think we're done with text. What I am having trouble with is the pdf converstion -- was working fine up until a few hours ago, and I don't think I changed any of the '\usepackage' stuff. I've tried in both LaTexian and TexShop and neither works. Also the references have started showing up as question marks.}

@@
